### 2025-03-05 tutorials/getstarted.qmd
Adress the remaining points.

```{julia}
using LieGroups, LinearAlgebra, RecursiveArrayTools
SO2 = SpecialOrthogonalGroup(2)
```

@@

```{julia}
SO3 = SpecialOrthogonalGroup(3)
g = [cos(π/3) -sin(π/3) 0.0; sin(π/3) cos(π/3) 0.0; 0.0 0.0 1.0]* [cos(π/4) 0.0 -sin(π/4); 0.0 1.0 0.0; sin(π/4) 0.0 cos(π/4)]
e = Matrix{Float64}(I,3,3)
g
```
The element `g` can be seen as a rotation by $π/3$ in the x-y-plane combined with a rotation by $π/4$ in the x-z plane.

@@

Consider the function of left group composition $λ_g(h) = g∘h$.
Its differential (or push forward) $Dλ_g(e)$ maps from $T_e𝒢$ to $T_g𝒢$
and is a linear bijection between both spaces.
Its adjoint differential (or pullback) $D^*λ_g(e)$ maps back from $T_g𝒢$ to $T_e𝒢$.

@@

since it is invariant if you use the differential of the left composition to identify tangent vectors.
We can even “spare” the pullbacks in this definition, when spring tangent vectors as their representants in the Lie algebra.
This is the default in `LieGroups.jl`.

@@

```{julia}
vee(LieAlgebra(SE3), gh1)
```

>>>>

```{julia}
using LieGroups, LinearAlgebra, RecursiveArrayTools, Rotations
SO2 = SpecialOrthogonalGroup(2)
```

@@

```{julia}
SO3 = SpecialOrthogonalGroup(3)
g = RotZ(π/3)*RotY(π/4)
e = Matrix{Float64}(I,3,3)
g
```
The element `g` can be seen as a rotation by $π/3$ in the x-y-plane combined with a rotation by $π/4$ in the x-z plane.

@@

Consider the function of left group composition $λ_g(h) = g∘h$.
Its ``[differential](@ref diff_left_compose(G::AbstractLieGroup, g, h, X))``{=commonmark} (or push forward) $Dλ_g(e)$ maps from $T_e𝒢$ to $T_g𝒢$
and is a linear bijection between both spaces.
Its adjoint differential (or pullback) $D^*λ_g(e)$ maps back from $T_g𝒢$ to $T_e𝒢$.

@@

since it is invariant if you use the differential of the left composition to identify tangent vectors.
We can even “spare” the pullbacks in this definition, when representing tangent vector alsways by their correspnding representants in the Lie algebra.
This is the default in `LieGroups.jl`.

Alternatively one can start with the right composition and its ``[differential](@ref diff_right_compose(G::AbstractLieGroup, h, g, X))``{=commonmark} to arrive an right-invariant vector fields and a right-invariant metric.

The left-invariant metric is in general not right-invariant, except for compact Lie groups and their direct products with Translations.

@@

```{julia}
vee(LieAlgebra(SE3), Y)
```
